Automated verification of stand-alone solar photovoltaic systems

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil e-mail alessandrotrindade@ufam.edu.br.}% <-this % stops a space
\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK e-mail lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
\thanks{Manuscript received September 19, 2018; revised November 26, 2018.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries. Particular attention is being given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible. Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulations that do not cover all the aspects of the design space. Automated verification using model checking, however, has proven to be an effective technique to program verification. Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, are encoded into a mathematical model, and a software model checking algorithm was developed to verify its design from a formal perspective. Case studies, from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro. Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach... this last sentence should be stronger to emphasise your main contribution... maybe you could update this after obtaining the experimental results...}
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Photovoltaic power systems, solar power generation, power system modeling, formal verification, model checking.
\end{IEEEkeywords}

@@

%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}. In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing \textcolor{red}{add citation here}.

@@

However, there is a main disadvantage of model checking: the state explosion problem. In order to tackle this problem, many different techniques were developed in the last decades. One of the first major advances was symbolic model checking with binary decision diagrams (BDDs). In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice. Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}. A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}. However, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.

@@

However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system, we identified that, in fact, the system mostly of the time does not meet the battery autonomy (mainly when all the loads are turned on). However, it is understandable that this problem occurs since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.

Related to the four 700 W PV systems, the sizing check was successful during automated verification, but flaws were found in all of them, all related with the battery autonomy, when SOC reached levels below 75\%. The automated verification identified the flaws right after the first night-discharge cycle, i.e., before the solar system starts recharging the batteries. The proposed method took 409.3 hours to find an error in house 1, and the maximum of \textcolor{red}{456XXX} hours to house 4. This functional problem \textcolor{red}{what is a functional problem?} was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------

We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions, in terms of temperature and solar irradiation, a PV system can fail. As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems. We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.

% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

>>>>

\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
\thanks{Manuscript received November 21, 2018; revised XXXXX 11, 2019.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible. Tools to evaluate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space. Automated verification using model checking has proven to be an effective technique to program verification. However, any kind of system can be verified by model checking, including the most complex. Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were encoded into a mathematical model, and a algorithm using model checking features was created in order to validate its design from a formal verification perspective. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro. Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach... this last sentence should be stronger to emphasise your main contribution... maybe you could update this after obtaining the experimental results...}
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Formal verification, model checking, photovoltaic power systems, power system modeling, solar power generation.
\end{IEEEkeywords}

@@

%Therefore, a wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves). However, the present work will rely on t
The simplified model of 1-diode has demonstrated that it has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}. In addition, this mathematical modeling has the advantage of being an explicit model, which does not use iterative numerical calculation, which is time-consuming to computing \cite{Cubas}.

@@

However, there is a main disadvantage of model checking: the state explosion problem. In order to tackle this problem, many different techniques were developed in the last decades. One of the first major advances was symbolic model checking with binary decision diagrams (BDDs). In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
% Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}. A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}. 
Meanwhile, one of the most promising approaches is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}.

@@

However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------
We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail. New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results from the houses that presented time-out condition. As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems. We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.
%
%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results. The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.
